%% Preamble stuff needed so that LaTeX can do the right thing
\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\begin{document}
%% Section enumerating upcoming tasks and task owners for roughly the next 24 hours
\section*{Next Goals and Deliverables}
\begin{itemize}
\item Implement Character Decoding - CLYK
\item Research Pathfinding Algorithms for Network (OSPF, DVR) - CLYK
\item Research Addressing Protocols - CLYK
\item Research on sending packets - CLYK

\end{itemize}
%% Section enumerating progress from the previous day. Items people were responsible for in the last progress report must appear. Additional tasks that the group agreed to add since the last progress report may be presented here. 
\section*{Previous Goals and Deliverables}
\begin{itemize}

\item Prompt user Multiple times for input - Luke (DONE) 
\item Read Multiple Transmissions one After Another - CLYK (in-progress)
\item Remove leading 1 from C12 - Caleb (DONE)
\item Complete Parity bit Error Detection - CLYK (DONE) (LinkLayer/Day8C11.c, Day8C12.c)
\item Lock threads with Mutex - CLYK (deferred)
\item Encode Characters into bits - Kyle (in-progress)
\item Submit Progress Update - (DONE) (Reports/ProgDay8.tex)
\end{itemize}
%% Sections above should be short bullets. Longer free form discussion of information from above goes here. These should still be short! More that a couple sentences and the discussion is better suited as a results write-up, appendix, or design document.
\section*{Discussion}
\begin{itemize}
\item Prompt user Multiple times for input - Using a while loop and cancelling it when a '2' is input, we're able to send multiple messages with a single run of the program.
\item Read Multiple Transmissions one after another - Likewise to above, we're able to read subsequent transmissions by leaving the thread open until a '2' is input by the user.
\item Remove Leading 1 from C12 - Our regularization function call was seemingly occurring too quickly before our listening thread started, resulting in an errant one on a single machine. Commenting this out has resolved our error.
\item Complete Parity bit Error Detection - We both add and detect a parity bit using an even number of 1s in order to detect an incorrect signal coming across in transmission.
\item Lock threads with Mutex - Since we solved the leading 1 on C12, we'll defer using Mutex for thread locking until it's necessary.
\item Encode Characters into bits - The strToBin function we wrote takes an array and its size and converts text characters to binary. Using it causes bit reception errors unfortunately, so more work needs done towards resolving this.

\end{itemize}
%% The appendix pages go here if there are any...
%\section*{Appendix}
%\begin{itemize}

%\end{itemize}

\end{document}